Collocated Snapshot Backup with VM-Centric Deduplication in the Cloud

### 2013-09-20 snapshot_system/fast14_evaluation.tex
updates to paper
paper revisions

\subsection{Impact on Fault Tolerance}
Figure~\ref{fig:vm-availability} shows the availability of VM snapshots when 
there are up to 25 storage nodes failed in a 1000-node cluster. 
Two VC curves use $V_c=1250$ and $V_c=2500$ representing the average number of VMs that share a PDS file system block. 
$V_c=2500$ represents  the absolute worst case for 2500 VMs. 
The VO curve has  $V_o=6.3$ which is the average number of VMs that share a file system block in our smaller dataset.
To get this number, we perform perfect deduplication over 105 VMs, append unique chunks to a DFS file and
count the number of dependencies from a file system block to VM.
In the scenario of having 2500 VMs, this number can only increase, thus this number represents the best
case for VO approach. 
Our results show that the VC approach even with $V_c=2500$ has a higher availability than VO.
For example, with 10 machines failed, VO with 98.5\% availability would lose snapshots of 37 VMs 
while VC with 99.9\% loses snapshots of 2.5 VMs.
The key reason is that  $N_1 +N_2 < N_o$, caused by the fact that the VM-centric approach localizes deduplication
and packs  data blocks for one VM as much as possible.  The extra replication
for PDS blocks also significantly increases the snapshot availability even when
a PDS file block is shared by every VM.

Figure~\ref{fig:pds-replication}
shows the snapshot availability when increasing the replication degree for PDS blocks. 
It can be seen that increasing the replication of 
the PDS blocks can have a good impact on the overall availability of the VM backups. 
PDS with more replication  makes up a small percent of the
stored data; however, the benefit to the snapshot availability is significant.

@@

\end{figure}

@@

Figure~\ref{fig:exbin-efficiency-graph2} shows the deduplication efficiency for SRB and VC.
% <<<<<<< HEAD
% Our deduplication efficiency is defined as the percent of duplicate chunks
% which are detected and deduplicated, so only global perfect deduplication can have 100\% efficiency.
% The figure also compares several PDS sizes chosen for VC. ``$\sigma=2\%$'' 
% is defined in Table~\ref{tab:symbol}. 
% =======
Deduplication efficiency is defined as the percent of duplicate chunks
which are detected and deduplicated, so only global perfect deduplication can have 100\% efficiency.
 We also compare several PDS sizes chosen for VC
(see Table~\ref{tab:symbol} for definition of ``$\sigma=2\%$'')
%we allocate the space of distributed shared memory  to accommodate 2\%
%of data chunks shared among VMs, as defined in 
With $\sigma=2\%$, memory usage for PDS index lookup per machine is about 100MB
and  the deduplication efficiency can reach over 96\%.
When $\sigma=4\%$, the deduplication efficiency can reach 97\%. 
The loss of efficiency in VC is caused by the restriction of the total physical memory available
in the cluster to support PDS index. 
In the extreme case if we put all the fingerprint into PDS 
index ($\sigma=100\%$) then VC will have 100\% efficiency.
The loss of efficiency in SRB is caused by the routing of data chunks which restricts the search scope
of duplicate detection.
Our VC approach delivers slightly worse deduplication efficiency compare to SRB, which is totally acceptable
because we are rewarded by architecture-wise benefits such as fault-tolerant and fast approximate deletion.

This result shows VC can remove  a competitive amount of duplicates.
In general, our experiments show that
dirty-bit detection at the segment level can reduce the data size to about 24\% of original data, 
which leads  about 76\% reduction.
Similarity-guided local search can further reduce the data size
to about 12\% of original size, namely it delivers additional 12\% reduction.
The PDS-based cross-VM detection with $\sigma=2\% $
can reduce the  size further to 5.6\% of original size, namely it 
delivers additional 6.4\% reduction.

>>>>

\subsection{Impact on Fault Tolerance}
Figure~\ref{tab:vm-availability} shows the availability of VM snapshots
as storage nodes fail. We assume a random distirbution of 64MB filesystem
blocks (FSBs). where FSBs are not randomly distributed availability might
be improved by limiting the number of storage nodes a particualr VM depends
on but we take the conservative approach. We compare VO, the expected case for
VC ($V_c=p*V/2$), and the worst case for VC ($V_c=p*V/2$). We set $V_o=6.3$
based on measured values in our dataset.
To get this number, we perform perfect deduplication over 105 VMs, append unique chunks to a DFS file and
count the number of dependencies from a file system block to VM.
In the case of having 2500 or even 25000 VMs, this number can only increase, thus this number represents the best
case for VO approach. 
Our results show that even the worst case for VC has a higher availability than VO.
By having extra replicas for the PDS data, we reduce the failure rate of PDS
FSBs enough that the failure rate for the VM approaches the failure rate of the
Non-PDS blocks. This minimizes the drop in availability between the expected
and worst case for VC.

Our VM-centric approach shows significant improvements
in VM availability.
For example, with 5/100 machines failed, VO with 93.3\% availability would lose data in 169 VMs 
while VC with 99.9\% loses data for 2 VMs.
The key reason is that for most data in VC ($1-\sigma$), only a single
VM can be affected by the loss of a single FSB, because our VM-centric approach
localizes deduplication.  Although the loss of a PDS block affects many VMs,
by increasing replication for those blocks we minimize the affect on VM
availability.

One of the advantages of VC is that there is a division between
popular and non-popular data to facilitate improved reliability. An important
consideration then is how much to increase PDS data replication. The additional
cost is relatively small, but based on our model we evaulated several
difference PDS replication factors (see Figure~\ref{fig:pds-replication}),
and found that beyond 6 replicas there is minimal improvement in data reliability.
This is because, as described before, the availability of the VM approaches the
availiability of the Non-PDS data as the failure rate of PDS data gets very small.
In the graph, the lines for $r_c=6$ and $r_c=9$ overlap because of this effect.

@@

\end{figure}
\begin{table}
    \footnotesize
    \tabcolsep=0.11cm
    \begin{tabular}{|l|l|l|l|l|l|l|}
        \hline
        \multirow{3}{*}{Failures}   & \multicolumn{6}{c|}{VM Availability} \\
                                    %\cline{2-7}
                                    & \multicolumn{3}{c|}{$p=100$} & \multicolumn{3}{c|}{$p=1000$} \\
                                    %\cline{2-7}
                                    & VO & VC & VC(WC) & VO & VC & VC(WC) \\
        \hline
        3 & 99.304 & 99.891 & 99.891 & 99.999 & 99.999 & 99.999\\
        5 & 93.256 & 98.919 & 98.919 & 99.993 & 99.999 & 99.999\\
        10 & 43.251 & 87.707 & 87.638 & 99.919 & 99.987 & 99.987\\
        20 & 0.034 & 24.953 & 21.571 & 99.228 & 99.879 & 99.879\\
        \hline
    \end{tabular}
    \caption{Availability of VM backups for VO and VC models. VC is shown
    for the expected and worst case (WC) values for $V_c$}
    \label{tab:vm-availability}
\end{table}

@@

Figure~\ref{fig:exbin-efficiency-graph2} shows the deduplication efficiency for SRB and VC.
% <<<<<<< HEAD
% Our deduplication efficiency is defined as the percent of duplicate chunks
% which are detected and deduplicated, so only global perfect deduplication can have 100\% efficiency.
% The figure also compares several PDS sizes chosen for VC. ``$\sigma=2\%$'' 
% is defined in Table~\ref{tab:symbol}. 
% =======
Deduplication efficiency is defined as the percent of duplicate chunks
which are detected and deduplicated, so only global perfect deduplication can have 100\% efficiency.
 We also compare several PDS sizes chosen for VC
(see Table~\ref{tab:symbol} for definition of ``$\sigma=2\%$'')
%we allocate the space of distributed shared memory  to accommodate 2\%
%of data chunks shared among VMs, as defined in 
With $\sigma=2\%$, memory usage for PDS index lookup per machine is about 100MB
and  the deduplication efficiency can reach over 96\%.
When $\sigma=4\%$, the deduplication efficiency can reach 97\%. 
The loss of efficiency in VC is caused by the restriction of the total physical memory available
in the cluster to support PDS index. 
In the extreme case if we put all the fingerprint into PDS 
index ($\sigma=100\%$) then VC will have 100\% efficiency.
The loss of efficiency in SRB is caused by the routing of data chunks which restricts the search scope
of duplicate detection.
SRB provides slightly better deduplication efficiency than our VC approach, which we accept
because we are rewarded by architecture-wise benefits such as fault-tolerance and fast approximate deletion.

Though not our primary goal, this result does show that VC can remove a competitive amount of duplicates.
In general, our experiments show that
dirty-bit detection at the segment level can reduce the data size to about 24\% of original data, 
which leads  about 76\% reduction.
Similarity-guided local search can further reduce the data size
to about 12\% of original size, namely it delivers additional 12\% reduction.
The PDS-based cross-VM detection with $\sigma=2\% $
can reduce the  size further to 5.6\% of original size, namely it 
delivers additional 6.4\% reduction.

Figure~\ref{fig:exbin-efficiency-graph2} also shows the benefits of our minhash
similar segment search in the parent snapshot. Without this, when an entire
segment is moved to another location on disk (e.g. when a file is rewritten
rather than modified in place), searching only the segment in the same location
in the parent will miss the deduplication opportunity. We have found that in
approximately 1/3 of the VMs in our dataset this movement happens frequently,
so the similarity search becomes important for those VMs.
